%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Tahir Bangash} \\ \vspace{1pt}
    \small \href{mailto:tahir.bangash8805@gmail.com}{\underline{tahir.bangash8805@gmail.com}} $|$ 
    \href{https://linkedin.com/in/tahir-bangash}{\underline{in/tahir-bangash}} $|$
    \href{https://github.com/tahirbangash}{\underline{github.com/tahirbangash}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {BASc in Computer Engineering - Co-op}{Sept. 2023 -- Apr. 2028}
      \resumeItemListStart
        \resumeItem{Term Dean's Honour List (Spring 2024) with a 96\% average.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Calian Group}{North York, ON}
      {Full-Stack Developer}{Jan. 2024 -- Dec. 2024}
      \resumeItemListStart
          \resumeItem{Expanded the application backend by developing \textbf{30+ RESTful API endpoints} using \textbf{Gin} and \textbf{Go}, enabling CRUD functionality for 6 new database tables and other existing ones.}
          \resumeItem{Designed and implemented database schemas with \textbf{GORM} to add support for new features and improve data organization.}
          \resumeItem{Created \textbf{30+ dynamic screens} using \textbf{React} and \textbf{TypeScript}, including forms and inputs for managing and viewing data to expand the app functionality.}
          \resumeItem{Implemented user authentication by building secure \textbf{login, multi-factor authentication (MFA)}, and password management pages, ensuring robust access control and data security.}
          \resumeItem{Implemented an organized state management system using \textbf{Redux}, ensuring consistency and efficiency across the application’s growing feature set.}
          \resumeItem{Reduced unnecessary re-renders by designing and implementing \textbf{React custom hooks}, improving performance and maintainability.}
        \resumeItemListEnd
          \resumeSubheading
      {Outlier}{Remote}
      {AI Reinforcement Learning Trainer}{Nov. 2024 -- Present}
      \resumeItemListStart
          \resumeItem{Trained AI models by evaluating and providing feedback on mathematical reasoning and problem-solving.}
          \resumeItem{Designed structured problem-solving prompts to guide AI towards more accurate and efficient responses.}
          \resumeItem{Developed and solved complex mathematical problems, offering step-by-step solutions to enhance AI understanding.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{University Apartment Subletting Platform} $|$ \emph{Flask, React, Go, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Developed a web application tailored for university students to sublet apartments during co-op terms}
            \resumeItem{Implemented secure user authentication and account management using Auth0.}
            \resumeItem{Designed and managed the backend using Go and GORM to support CRUD operations and database interactions.}
            \resumeItem{Utilized PostgreSQL for database management, to store relevant data on accounts and postings.}
            \resumeItem{Integrated AWS S3 for secure image and video storage.}
            \resumeItem{Built a responsive front end using React and TypeScript to enable users to create and browse listings seamlessly.}
            \resumeItem{Build a service with flask for rendering a static info page for a shared listing.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AI Digit Recognition} $|$ \emph{TensorFlow, OpenCV}}{}
          \resumeItemListStart
            \resumeItem{Developed an AI model to classify handwritten digits using TensorFlow.}
            \resumeItem{Utilized OpenCV for image preprocessing to improve model accuracy.}
            \resumeItem{Designed and trained a neural network from scratch for digit recognition.}
          \resumeItemListEnd
      \resumeProjectHeading
    {\textbf{Word Puzzle Solver} $|$ \emph{Flask, Python, Algorithms}}{}
    \resumeItemListStart
        \resumeItem{Developed a Flask-based web application to efficiently solve Word Hunt puzzles.}
            \resumeItem{Implemented a Trie data structure to store a dictionary of English words, enabling efficient DFS traversal of a 4x4 letter grid.}
            \resumeItem{Optimized search performance by pruning invalid paths early, improving speed compared to brute-force methods.}
            \resumeItem{Designed and implemented HTML/CSS templates for user-friendly input and result display.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Back End}{: Python, Java, Go, C++, Node.js, Express, Gin, Flask} \\
     \textbf{Front End}{: JavaScript, HTML, CSS, React, Redux} \\
     \textbf{Databases}{: SQL, PostgreSQL} \\
     \textbf{Tools and Platforms}{: GitHub, Postman, Docker}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
