%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Tahir Bangash} \\ \vspace{1pt}
    \small \href{mailto:tahir.bangash8805@gmail.com}{\underline{tahir.bangash8805@gmail.com}} $|$ 
    \href{https://linkedin.com/in/tahir-bangash}{\underline{in/tahir-bangash}} $|$
    \href{https://github.com/tahirbangash}{\underline{github.com/tahirbangash}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {BASc in Computer Engineering - Co-op}{Sept. 2023 -- Apr. 2028}
      \resumeItemListStart
        \resumeItem{Term Dean's Honour List (Spring 2024); cumulative GPA: 92\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Elbe AI}{Toronto, ON}
      {Full-Stack Developer | 4 month co-op}{May 2025 -- Aug. 2025}
      \resumeItemListStart
          \resumeItem{Expanded features from single-party to \textbf{multi-party collaboration}, enabling broader platform adoption.}
          \resumeItem{Designed and implemented \textbf{version control} with conflict handling to sync counterparties’ data reliably.}
          \resumeItem{Built new \textbf{Next.js (TypeScript)} pages and components integrated with \textbf{Firebase APIs}.}
          \resumeItem{Improved automated report generation by refactoring code to reorganize element structure and resolve layout bugs, enhancing clarity and consistency of generated reports.}
      
      \resumeItemListEnd

    \resumeSubheading
      {Calian Group}{North York, ON}
      {Full-Stack Developer | 2 co-ops with part time in-between}{Jan. 2024 -- Dec. 2024}
      \resumeItemListStart
          \resumeItem{Expanded the backend by implementing \textbf{30+ RESTful API endpoints} using \textbf{Gin} and \textbf{Go}, enabling CRUD functionality for 6 new database tables and other existing ones.}
          \resumeItem{Implemented \textbf{database schemas} to add support for new features and improve data organization.}
          \resumeItem{Created \textbf{30+ dynamic screens} using \textbf{React} and \textbf{TypeScript} to expand the app functionality.}
          \resumeItem{Implemented an organized state management system using \textbf{Redux}, improving consistency and organization.}
          \resumeItem{Refactored existing React components to implement custom hooks, improving code organization, reusability, and reducing unnecessary re-renders across the app.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{University Apartment Subletting Platform} $|$ \emph{Flask, React, Go, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application tailored for university students to sublet apartments during co-op terms}
            \resumeItem{Developed backend with Go and PostgreSQL.}
            \resumeItem{Built a responsive front end using React and TypeScript to enable users to create and browse listings seamlessly.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{World Bank Time Series Data Processor} $|$ \emph{C++}}{}
          \resumeItemListStart
            \resumeItem{Developed a C++ system to efficiently organize and analyze large World Bank time series datasets.}
            \resumeItem{Implemented data structures such as trees and maps to enable fast retrieval and complex data comparisons.}
            \resumeItem{Designed querying methods to identify countries meeting specific statistical conditions and compute aggregated results efficiently.}
          \resumeItemListEnd
          
      \resumeProjectHeading
        {\textbf{PNG File Processing Tools} $|$ \emph{C, Linux, File I/O, System Programming}}{}
        \resumeItemListStart
            \resumeItem{Created functions to identify valid PNG files and to concatenate horizontal image strips into a single image.}
            \resumeItem{Parsed PNG headers and data chunks, handling binary RGBA data and checking for CRC errors in files.}
            \resumeItem{Used Linux system calls and standard C file I/O to traverse directories, and read/write binary files.}
        \resumeItemListEnd

          
      \resumeProjectHeading
          {\textbf{Home HVAC Control System on FPGA} $|$ \emph{VHDL, FPGA, Digital Logic}}{}
          \resumeItemListStart
            \resumeItem{Developed a smart home HVAC system on an FPGA, capable of adjusting temperature based on sensor input.}
            \resumeItem{Designed control logic for heating, cooling, and fan systems with real-time updates.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Morse Code Converter in Assembly} $|$ \emph{RISC-V, Assembly, Embedded Systems}}{}
          \resumeItemListStart
            \resumeItem{Developed an assembly program that converts input text into Morse code.}
            \resumeItem{Implemented LED blinking patterns to represent Morse code output.}
          \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Terminal Minesweeper Game} $|$ \emph{C++}}{}
        \resumeItemListStart
            \resumeItem{Developed a fully playable Minesweeper game in the terminal using C++.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Back End}{: Python, Go, C, C++, Node.js, Express, Flask, SQL} \\
     \textbf{Front End}{: JavaScript, TypeScript, HTML, CSS, Next.js, React, Redux} \\
     \textbf{Databases}{: PostgreSQL} \\
     \textbf{Tools and Platforms}{: GitHub, Postman, GitLab, Linear}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
