%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{fontawesome5}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Tahir Bangash} \\[7.5pt]
\href{https://github.com/tahirbangash}{\raisebox{-0.05\height}\faGithub\ username} \ $|$ \ 
\href{https://linkedin.com/in/tahir-bangash-a1318a229/}{\raisebox{-0.05\height}\faLinkedin\ username} \ $|$ \
\href{mailto:tbangash@uwaterloo.ca}{\raisebox{-0.05\height}\faEnvelope \ tbangash@uwaterloo.ca} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\textbf{Back end:} Python, Java, Go, C++, Node.js, Express, Gin, Git, GORM \\
\textbf{Front end:} JavaScript, HTML, CSS, React, Redux \\
\textbf{Databases:} SQL, PostgreSQL

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\begin{tabularx}{\linewidth}{@{}l X@{}}	
\textbf{University of Waterloo} & \hfill Sept 2023 - April 2028 \\
\multicolumn{2}{@{}X@{}}{BASc Computer Engineering - Co op} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Full-Stack Developer Intern, Calian , NorthYork, Canada } & \hfill Jan 2024 - Present \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
    \item Developed and maintained company web apps using React, TypeScript, HTML, CSS, Redux, and libraries such as ANTDesign and Bootstrap
    \item Developed the backend using Go with Gin and Gorm to create APIs to preform CRUD oeprations on Postgress DB
    \item Collaborated with a team of developers to implement new features and improve existing codebase.
\end{itemize}
} \\
\end{tabularx}



%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------

\section*{Projects}
\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{Mock Dealership Website} & \href{https://yourprojectlink.com}{View Project} \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item Developed a microservice architecture with a React frontend.
    \item Implemented two backend services: one in Node.js and Express (containerized), another in Django using MongoDB.
    \item Integrated IBM Watson AI for sentiment analysis on customer reviews.
\end{itemize}
} \\

\textbf{Word Hunt Solution Algorithm} & \href{http://tahirbangash.pythonanywhere.com}{View Project} \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item Created a Flask web application to generate solutions for the game Word Hunt
    \item Wrote a DFS algorithm to find all valid word chains
    \item Built a UI for inputting the game puzzle, and for viewing results
\end{itemize}
} \\

\textbf{Weather App} & \href{https://tahirbangash.github.io/react_real_time_weather_app/}{View Project} \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item Built a React and JavaScript application that utilizes a free weather API.
    \item Features search functionality to display weather by region.
    \item Implemented location API to initially load a users current location.
\end{itemize}
} \\

\subsection*{Additional Projects}
\textbf{Frontend Projects} & \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item \textbf{Portfolio (HTML) :} Built a personal portfolio webpage using JS, HTML, and CSS.
    \item \textbf{Todo List (React):} Developed a dynamic todo list application, allowing users to manage tasks interactively.
    \item \textbf{Shipping Cost Calculator (React):} Created an application to calculate shipping costs based on various parameters.
\end{itemize}
} \\

\textbf{Backend Projects} & \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item \textbf{Book Reviews API (Node.js \& Express):} Designed an API endpoint for handling CRUD operations on book reviews.
    \item \textbf{Posts Management API (Go, Gin, GORM, \& PostgreSQL):} Built a robust backend API for creating and managing posts with full CRUD operations.
\end{itemize}
} \\

\end{tabularx}

%----------------------------------------------------------------------------------------
% VOLUNTEER WORK
%----------------------------------------------------------------------------------------
\section{Volunteer Work}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Event Planning, MYNA Canada} & \hfill May 2019 - August 2023 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
    \item Created budgets for events over \$60K, such as summer camps and other overnight events.
    \item Used Notion, Excel, Docs, and Canva to create detailed programs for various events.
    \item Led teams for multiple events, including a 5-day overnight summer camp and a ski trip.
\end{itemize}
} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% AWARDS
%----------------------------------------------------------------------------------------
\section{Awards}
\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{AP Scholar Award, College Board, USA} & June 2022 \\
\multicolumn{2}{@{}X@{}}{Awarded to students achieving a score of 3 or higher on three or more AP exams.} \\
\textbf{Certificate of Distinction, The University of Waterloo, ON} & 2022, 2023 \\
\multicolumn{2}{@{}X@{}}{Awarded to students finishing in the top 25\% of contest writers for the Waterloo math contests.} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{IBM Full-Stack Developer Certification} & May 2024 \\
\multicolumn{2}{@{}X@{}}{This certification program covered a range of topics including advanced full-stack development techniques, focusing on both front-end and back-end technologies.} \\
\end{tabularx}



\vfill
\center{\footnotesize Last updated: \today}

\end{document}

